### 2019-10-01 banking.tex

>>>>

\paragraph{Tax Exemption} will be discussed with meeting planning staff at
ANS Headquarters. The University of Illinois is tax exempt in the state of Illinois. 
Additionally, we will work driectly with ANS Headquarters to ensure tax 
exemption. Since ANS is incorporated under the General Not for Profit 
Corporation Act of Illinois, we expect this will be straightforward. We 
additionally expect such discussions will be facilitated by the physical 
proximity of ANS Headquarters and the University of Illinois (a 2 hour drive).

### 2019-10-01 budget.tex

\subsection{Cost of Attendance and Student Reimbursement}
The cost of attending the student conference, per student, varies among schools and is highly dependent on distance from UIUC and the preferred mode of travel. We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is assumed to be double the number of beds. The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. While some students may wish to make use of the convenience of the local airport, in general the most economic method of arriving in Champaign is by first flying to O’Hare and then busing. The average cost of this trip comes out to be \$293 as shown in Table  \ref{table:airfare}. Adding this to the registration and lodging costs (see Table \ref{table:hotels}) for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$447. The travel reimbursement is meant to help mitigate some or most of the costs for students coming to this conference to encourage future attendance at other conferences.

>>>>

\subsection{Cost of Attendance and Student Reimbursement}
The cost of attending the student conference, per student, varies among schools 
and is highly dependent on distance from UIUC and the preferred mode of travel. 
We will assume that minimizing cost is a priority for schools, thus number of 
persons per hotel room is assumed to be double the number of beds. The 
University of Illinois is a 2.5 hour drive from one of the largest airports in 
the world, O'Hare International Airport. There is also a small airport located 
just 15 minutes outside of campus which has regular flights to Chicago O'Hare 
(ORD), Dallas/Fort Worth (DFW), and Charlotte (CLT). While some students may 
wish to make use of the convenience of the local airport, in general the most 
economic method of arriving in Champaign is by first flying to O’Hare and then 
busing. The average cost of this trip comes out to be \$293 as shown in Table  
\ref{table:airfare}. Adding this to the registration and lodging costs (see 
Table \ref{table:hotels}) for four nights (as students often arrive Wednesday 
evening) and assuming four students per room, \textbf{the total cost of attendance for 
each student comes out to an average of \$447.} The travel reimbursement is 
meant to help mitigate some or most of the costs for students coming to this 
conference to encourage future attendance at other conferences.
